QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-2.2.tex
replace format by form, fix some grammar
- format could mean that we include the original files, which we do not do

\textcolor{red}{
Furthermore, as previously remarked, a not (positive or negative) definite $Q^i$ does not necessarily correspond to a nonconvex feasible region. For instance, it is well-known that Second-Order Cone Programs have convex feasible regions; when represented in terms of quadratic constraints, however, they correspond to $Q^i$ with one negative eigenvalue. In our taxonomy we still consider the corresponding instances as \textit{**Q} ones, with no attempt to detect the different special structures that actually correspond to convex feasible regions. Although this may lead to classify as ``potentially nonconvex'' some instances that are in fact convex, our choice is justified by the fact that not all QP solvers are capable of detecting and exploiting these structures, which means that the instance can actually be treated as a nonconvex one even if it is not.\\
}
\textcolor{red}{
One of the nontrivial choices in our library is that we made no effort to reformulate the instances, and inserted them in the library in the very same format they have been provided to us by the original contributors. The rationale of this choice is that reformulation techniques, like the ones discussed here and others, are typically motivated by the fact that they make the instance easier to solve for one specific class of solvers. This being a bias that we don’t want to add we have chosen to keep the instances in their ``natural'' format, this being the one in which the original contributor initially wrote them.
}

>>>>

\textcolor{red}{
Furthermore, as previously remarked, a not (positive or negative) definite $Q^i$ does not necessarily correspond to a nonconvex feasible region. For instance, it is well-known that Second-Order Cone Programs have convex feasible regions; when represented in terms of quadratic constraints, however, they correspond to $Q^i$ with one negative eigenvalue. In our taxonomy we still consider the corresponding instances as \textit{**Q} ones, with no attempt to detect the different special structures that actually correspond to convex feasible regions. Although this may lead to classify as ``potentially nonconvex'' some instances that are in fact convex, our choice is justified by the fact that not all QP solvers are capable of detecting and exploiting these structures, which means that the instance can actually be treated as a nonconvex one even if it is not.\\
}
\textcolor{red}{
One of the nontrivial choices in our library is that we made no effort to reformulate the instances, and inserted them in the library in the very same form as they have been provided to us by the original contributors. The rationale of this choice is that reformulation techniques, like the ones discussed here and others, are typically motivated by the fact that they make the instance easier to solve for one specific class of solvers. This being a bias that we do not want to add we have chosen to keep the instances in their ``natural'' form, this being the one in which the original contributor initially wrote them.
}
